---
title: "Reproducible Pitch Presentation"
author: "Steven Hanssens"
date: "20/06/2021"
output: slidy_presentation
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source('~/MyShinyAndPitch/MyScript.R')
library(shiny)
```

## 2020 Car crash data in Belgium

Our application uses data about car crashs in Belgium during the year 2020. These data are available [here](https://statbel.fgov.be/fr/open-data/accidents-de-la-circulation-2020). The application provides visualization about car accidents in Belgium in 2020.


You can find it, on ShinyApps.io, [here](http://hsteven1406.shinyapps.io/RoadAccident) and its repository, on Github, [there](https://github.com/HSteven1406/MyShinyAndPitch).

## Variables used
In the next slide, we will show our cleaned dataset. But, first, let me explain the variables used : 

- Region = Regions in Belgium
- Prov = Provinces in Belgium
- ACCT = number of accidents
- DEAD = number of accidents causing immediate deaths
- DEAD_30_DAYS = number of accidents causing deaths within 30 days
- MORTALLY_INJ = number of accidents causing mortally injuries
- SERLY_INJ = number of accidents causing serious injuries
- SLY_INJ = number of accidents causing minor injuries


## Exploratory Analysis

After cleaning, here is the data used for my application

```{r}
SumData
```

 
## The App
```{r, echo=FALSE}
shinyAppDir("~/MyShinyAndPitch/RoadAccident")
```

